\section{Simulation Setup}

The Rabot outdoor scenario is defined in \texttt{scenarios/rabot.yaml}. The scene is derived from an \gls{osm} boundary around the KU Leuven Gent Campus Rabot environment. Candidate distributed-\gls{ap} positions are generated along building walls at low height, one rooftop proxy is reserved for the central reference strategy, and user mobility is simulated over the outdoor walkable area with mixed pedestrian and bicycle profiles.

The simulation workflow used by the paper matches the repository workflow:
\begin{enumerate}
    \item build the outdoor scene and walk graph from \gls{osm},
    \item generate wall-mounted candidate \glspl{ap} and the single rooftop proxy site,
    \item simulate user trajectories over the walkable outdoor area,
    \item compute path-based \gls{csi} and explicit \gls{sinr} terms,
    \item compare the central proxy, the fixed distributed baseline, the nearest-user proxy-\gls{esr} rule, and the nearest-user proxy-power rule,
    \item export reusable result files,
    \item generate analysis figures in a separate postprocessing step.
\end{enumerate}

This section documents the reproducible processing chain from scene generation to postprocessed figure export. The antenna configuration is kept fixed across all placement strategies at the element-model level: the simulator instantiates \gls{upa}-based node arrays with the \gls{3gpp} \texttt{tr38901} element pattern, half-wavelength spacing in both planar dimensions, and \texttt{VH} dual polarization. The distributed strategies use identical $2\times 3$ wall-mounted \glspl{ap}, whereas the central reference aggregates that same element budget into one normalized co-located rooftop $6\times 6$ array with summed transmit power. Consequently, the comparison isolates the effect of geometry, relocation, and distributed-versus-co-located topology while keeping the underlying element directivity model unchanged.

\begin{table}[t]
    \centering
    \caption{Key Rabot scenario parameters used in the Rabot simulations.}
    \label{tab:rabot_setup}
    \begin{tabular}{ll}
        \toprule
        Parameter & Value \\
        \midrule
        Carrier frequency & \SI{3.5}{\giga\hertz} \\
        Bandwidth & \SI{100}{\mega\hertz} \\
        AP array topology & $2 \times 3$ \gls{upa}, dual-polarized \texttt{VH} \\
        Central proxy topology & normalized co-located $6 \times 6$ \gls{upa}, dual-polarized \texttt{VH} \\
        UE array topology & $1 \times 1$ planar array, dual-polarized \texttt{VH} \\
        Element spacing & $0.5\lambda$ vertical, $0.5\lambda$ horizontal \\
        Element radiation pattern & \gls{3gpp} \texttt{tr38901} \\
        User height & \SI{1.5}{\meter} \\
        Number of users & 10 \\
        Simulation horizon & \SI{3600}{\second} \\
        Time step & \SI{5}{\second} \\
        Distributed \glspl{ap} per strategy & 6 \\
        Fixed distributed \glspl{ap} & 0 \\
        Candidate wall height & \SI{1.5}{\meter} \\
        Candidate wall spacing & \SI{18}{\meter} \\
        Minimum candidate spacing dth & \SI{12}{\meter} \\
        Candidate wall offset & \SI{0.25}{\meter} \\
        Relocation window Trel & \SI{60}{\second} \\
        Optimization distance threshold & \SI{25}{\meter} \\
        % Initialization seed & 11 \\
        % Compared strategies & central proxy, fixed distributed, movable distributed opt.~2, opt.~3 \\
        % Coverage maps & disabled in current Rabot config \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{table}[t]
    \centering
    \caption{Placement-strategy definitions used throughout the article.}
    \label{tab:placement_algorithms}
    \begin{tabular}{p{0.20\linewidth}p{0.72\linewidth}}
        \toprule
        Strategy & Description \\
        \midrule
        \texttt{central\_massive\_mimo} & Single rooftop proxy on the building nearest the area center, oriented toward the center, with a normalized co-located $6\times 6$ \gls{upa} obtained by aggregating the distributed element budget into one rooftop site. Use as central reference only. \\
        \texttt{distributed\_fixed} & One distributed subset is selected from wall candidates and kept unchanged for the full run. \\
        \texttt{distributed\_movable\_optimization\_2} & Optimization~2. The distributed subset is reselected every relocation window from a nearest-user \gls{ue}-to-\gls{ue} proxy-\gls{csi} model: each candidate site binds to the closest user within the configured distance threshold, the code forms a wideband proxy channel from that user's measured \gls{ue}-to-\gls{ue} CFR, and the subset is ranked by proxy \gls{esr}. \\
        \texttt{distributed\_movable\_optimization\_3} & Optimization~3. The distributed subset is reselected every relocation window from the same nearest-user distance-threshold proxy model as optimization~2, but the code uses the stored \gls{ue}-to-\gls{ue} link-power row of the anchor user, replaces the diagonal entry by the strongest non-self value, rescales by $P_{\mathrm{AP}}/P_{\mathrm{UE}}$, and ranks the subset by proxy average power. \\
        \bottomrule
    \end{tabular}
\end{table}

The figure set in \cref{sec:results_geometry,sec:results_sinr,sec:results_relocation} is read directly from the generated Rabot outputs under \texttt{outputs/rabot/} and \texttt{outputs/rabot/postprocessing/}. This keeps the manuscript synchronized with the latest postprocessed result files in the repository.

For the current Rabot instantiation, the relocation controller starts from a single seed constellation drawn from the wall-mounted candidate pool using the configured random seed. That seed constellation is frozen for the \texttt{distributed\_fixed} baseline and also provides the initial labeled movable-\gls{ap} positions for \texttt{distributed\_movable\_optimization\_2} and \texttt{distributed\_movable\_optimization\_3}. Thereafter, every relocation window applies the greedy subset search from \cref{sec:system_model} with the selected proxy objective and then solves a minimum-displacement assignment so that schedule traces, relocation distances, and move fractions correspond to the motion of persistent AP identities rather than to arbitrary reordering of candidate sites. The current implementation is trace-driven: at the start of a relocation window, the selector uses the simulated user positions and \gls{ue}-to-\gls{ue} proxy measurements over that same window as short-horizon look-ahead information. For optimization~2 and optimization~3, the dormant candidate-position \gls{ap}-to-\gls{ue} channel is never queried during this search; only measured \gls{ue}-to-\gls{ue} proxy information is used. Optimization~2 prefers the full complex wideband proxy channel and falls back to a power-based proxy-\gls{esr} computation when that proxy channel cannot be decoded robustly from the exported tensor. Optimization~3 always uses the stored proxy link-power tensor. In all cases, the actual deployed \gls{ap}-to-\gls{ue} \gls{csi} is recomputed only after the new candidate subset has been selected.
