\section{Discussion and Current Limits}

The present study has several modeling and evaluation limits that define the scope of the reported results.

Two findings stand out from the Rabot results. First, distributed wall-mounted deployments are consistently superior to the normalized central rooftop proxy in this scenario. Even \strategy2[title] improves both average and lower-tail performance over \strategy1[title], which indicates that the spatially spread outdoor user process benefits strongly from nearby façade-mounted service points. Second, the quality of the relocation proxy matters more than relocation alone. \strategy4[title] outperforms \strategy5[title] on all reported radio metrics while also requiring less movement, which shows that phase-aware \gls{ue}-to-\gls{ue} proxy \gls{csi} carries useful information beyond power-only proxy measurements.

The main limitations are the following:
\begin{itemize}
    \item Only a single outdoor scenario is considered.
    \item The central massive-\gls{mimo} comparison point is a rooftop proxy, not a full placement model for one true co-located massive-\gls{mimo} array.
    \item The movable optimization results use trace-driven current-window look-ahead in the \gls{ue}-to-\gls{ue} proxy measurements. They should therefore be read as a window-level relocation benchmark, not as a strictly causal online controller.
    \item The relocation analysis reports aggregate movement burden rather than attributing marginal \gls{esr} gain to individual moves; this would require counterfactual no-move comparisons at each relocation instant.
    \item The current Rabot configuration disables coverage-map exports, so the paper centers on trajectory-level \gls{sinr} and schedule metrics.
    \item Citizen participation is abstracted as movable candidate positions and scheduler actions rather than being validated experimentally.
    \item Sensitivity to random seeds, scenario perturbations, and broader deployment-cost models is not yet characterized.
\end{itemize}

These limitations motivate extensions toward multi-scenario studies, sensitivity analyses, coverage-map reporting, and eventual experimental validation in co-created deployments.
