\section{Conclusion}

This article presented a simulation-based study of low-height distributed-\gls{mimo} access networks with repositionable infrastructure in an outdoor urban scenario. The paper combined a system model, two proxy-based relocation algorithms, a reproducible Rabot simulation workflow, and postprocessed geometry, \gls{sinr}, \gls{esr}, and relocation figures derived from exported artifacts. The movable strategies span a nearest-user \gls{ue}-to-\gls{ue} proxy-\gls{csi} controller with a proxy-\gls{esr} objective and a nearest-user proxy-power controller that ranks subsets from stored \gls{ue}-to-\gls{ue} link-power samples scaled to the \gls{ap} transmit-power budget.

For the Rabot dataset, \strategy4[title] is the best overall strategy. It yields the highest mean and lower-tail \gls{sinr}/\gls{esr}, reduces outage most strongly, and does so with less movement than \strategy5[title]. \strategy5[title] remains clearly beneficial relative to \strategy2[title] in mean-rate terms, but it does not improve the outage tail and requires the largest relocation effort. \strategy2[title] remains the strongest zero-relocation option, while \strategy1[title] is the weakest reference in this scenario.

Within its current scope, the framework supports systematic comparison of a central rooftop proxy, a fixed distributed deployment, and two relocation-capable distributed deployments under a common channel model and mobility process. Natural next steps are multi-scenario studies, coverage-map analysis, sensitivity analysis for the proxy-based relocation rules, and experimental validation in the broader Cocoon program.
